### 2017-11-21 manuscript.rmd
fixed issues with dpruned_data matching species names

#Depth pruned data
dpruned_data = cdata[which(!is.na(cdata$Depth.Median)), ]
dpruned_tree <- drop.tip(ultratree, which(!(tree$tip.label %in% rownames(dpruned_data))))
dpruned_data <- dpruned_data[match(dpruned_tree$tip.label, rownames(dpruned_data)),]

>>>>

#Depth pruned data
dpruned_data = cdata[which(!is.na(cdata$Depth.Median)), ]
dpruned_tree <- drop.tip(ultratree, which(!(ultratree$tip.label %in% rownames(dpruned_data))))
dpruned_data <- dpruned_data[match(dpruned_tree$tip.label, rownames(dpruned_data)),]
